---
title: "Scraper"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(rvest)
library(stringr)
library(readxl)

# Helper function to clean the legislator's name
# NO LONGER NEEDED
name_cleaner <- function(name){
  name <- gsub("U.S. Representative", "", name)
  name <- gsub("Representative", "", name)
  name <- gsub("U.S. Congressman", "", name)
  name <- gsub("U.S. Congresswoman", "", name)
  name <- gsub("Congressman", "", name)
  name <- gsub("Congresswoman", "", name)
  name <- gsub("Home - ", "", name)
  name <- gsub("\\s*,?\\s*(D\\.D\\.S\\.|PhD|M\\.D\\.|M\\.Sc\\.|LL\\.M\\.|
               J\\.D\\.|B\\.Sc\\.|D\\.Phil\\.|Ed\\.D\\.|M\\.Eng\\.|\\w{1,3}
               \\.\\w{1,3}\\.)", "", name) # Remove degrees but keep things like Jr.
  name <- str_trim(name)
  
  return(name)
}
```

# Getting House links
```{r}
house_links <- read_html("https://www.house.gov/representatives") %>% 
  html_elements(".views-field-value-5 a") %>% 
  html_attr("href") %>% 
  sapply(FUN=function(x) sub("(house\\.gov).*", "\\1", x)) # Clean junk tacked on the end

house_names <- read_html("https://www.house.gov/representatives") %>% 
  html_elements(".views-field-value-5 a") %>% 
  html_text() %>% str_trim()

names(house_links) <- house_names
```

# Scraper v2

## Helpers

### Date format detector
```{r}
# Helper function to detect date formats for a list of strings
detect_date_formats <- function(date_strings) {
  # A list of candidate formats (date-only and datetime variants)
  candidate_formats <- c(
    "%Y-%m-%dT%H:%M:%S",   # ISO 8601 with T separator
    "%Y-%m-%d %H:%M:%S",   # Common datetime with space separator
    "%Y-%m-%d",            # ISO date
    "%d/%m/%Y %H:%M:%S",   # Day/Month/Year with datetime
    "%d/%m/%Y",            # Day/Month/Year
    "%m/%d/%Y %H:%M:%S",   # Month/Day/Year with datetime
    "%m/%d/%Y",            # Month/Day/Year
    "%Y/%m/%d %H:%M:%S",   # Year/Month/Day with datetime using slash
    "%Y/%m/%d",            # Year/Month/Day with slash
    
    # Full month name formats like "September 23, 2020"
    "%B %d, %Y",
    "%B %d %Y",
    "%B %d, %Y %H:%M:%S",

    # Abbreviated month name formats like "Sep 23, 2021" (without a period)
    "%b %d, %Y",
    "%b %d, %Y %H:%M:%S",
    
    # Abbreviated month name with a period: "Sep. 23, 2021"
    "%b. %d, %Y",
    "%b. %d, %Y %H:%M:%S"
  )
  
  # Function to clean ordinal suffixes (st, nd, rd, th) from date strings
  clean_ordinal_suffixes <- function(date_str) {
    gsub("(\\d{1,2})(st|nd|rd|th)", "\\1", date_str, perl = TRUE)
  }
  
  # For each string in date_strings, find the first format (if any) that parses successfully
  sapply(date_strings, function(ds) {
    fmt_found <- NA_character_
    
    # Remove ordinal suffixes before checking formats
    cleaned_ds <- clean_ordinal_suffixes(ds)
    
    for (fmt in candidate_formats) {
      parsed <- suppressWarnings(strptime(cleaned_ds, format = fmt))
      if (!is.na(parsed)) {
        fmt_found <- fmt
        break
      }
    }
    
    fmt_found
  })
}

```


### PR link formatter
```{r}
format_pr_link <- function(pr_links, pr_page_link) {
  url_pattern <- "^https?://[[:alnum:]._/-]+$"
  
  # Ensure pr_links is treated as a vector
  if (!is.vector(pr_links)) pr_links <- c(pr_links)
  
  # Function to extract the base path from a URL (excluding domain)
  extract_base_path <- function(url) {
    parts <- unlist(strsplit(url, "/"))
    if (length(parts) > 3) {
      return(paste(parts[4:length(parts)], collapse = "/"))  # Extract everything after domain
    }
    return("")
  }
  
  # Function to extract just the domain from a URL
  extract_domain <- function(url) {
    parts <- unlist(strsplit(url, "/"))
    if (length(parts) >= 3) {
      return(paste(parts[1:3], collapse = "/"))  # Extract "https://site.com"
    }
    return(url)  # Return unchanged if something goes wrong
  }
  
  # Function to extract the parent path (i.e., the directory) from a full URL
  extract_parent_path <- function(url) {
    url_no_query <- sub("\\?.*$", "", url)  # Remove query parameters
    return(dirname(url_no_query))  # Get directory path
  }
  
  # Extract components of pr_page_link
  pr_page_base <- extract_base_path(pr_page_link)
  pr_page_domain <- extract_domain(pr_page_link)
  pr_page_parent <- extract_parent_path(pr_page_link)
  
  # Extract base paths from pr_links
  pr_links_bases <- unique(sapply(pr_links, extract_base_path))  # Get unique base paths
  
  # If pr_links has a more reliable base path, use it
  if (length(pr_links_bases) > 0 && pr_page_base %in% pr_links_bases == FALSE) {
    preferred_base <- dirname(pr_links_bases[1])  # Get directory path
    pr_page_link <- paste0(pr_page_domain, "/", preferred_base)  # Reconstruct pr_page_link with the new base
  }
  
  # Process each link correctly
  retVal <- sapply(pr_links, 
                   FUN = function(x) {
                     if (grepl(url_pattern, x)) {
                       return(x)  # Already absolute URL, return as is
                     } else if (grepl("^\\?", x) || grepl("documentsingle.aspx", x)) {
                       # If it's a query-style link like "?DocumentID=4060" or "documentsingle.aspx",
                       # it should inherit the parent directory of pr_page_link.
                       return(paste0(pr_page_parent, "/", x))
                     } else {
                       # Ensure it is properly appended to the corrected base path
                       return(url_absolute(x, pr_page_link))
                     }
                   })
  
  names(retVal) <- NULL
  return(retVal[!is.na(retVal)])
}

# format_pr_link("/2025/3/rep-sewell-introduces-the-john-r-lewis-voting-rights-advancement-act-ahead-of-the-60th-anniversary-of-bloody-sunday",
#                 "https://sewell.house.gov/media/press-releases")


# format_pr_link("/media-center/press-releases/amata-s-igia-message-calls-fishing-restoration-and-remember-us",
#                "https://radewagen.house.gov/media/press-releases")
# 
# format_pr_link("documentsingle.aspx?DocumentID=4060",
#                 "https://mikerogers.house.gov/news/documentquery.aspx?DocumentTypeID=27")
# 
# format_pr_link("documentsingle.aspx?DocumentID=4060",
#                 "https://mikerogers.house.gov/news/?page=1")
# 
# format_pr_link("/media/press-releases/steil-issues-statement-on-president-trump-s-address-to-the-joint-session-of-congress",
#                "https://steil.house.gov/media/press-releases")
```

## Main functions

### Presser page finder
```{r}
presser_page_finder <- function(link, debug = FALSE) {
  trim_slash <- function(x) sub("/+$", "", x)
  
  # Expanded list of known subdirectories for press releases
  possible_subdirs <- c(
    "press-release", "press-releases", "pressroom", "press-room",
    "category/congress_press_release", "category/press-release", "category/press-releases"
  )
  
  # Function to safely read an HTML page
  try_read_html <- function(url) {
    tryCatch(
      read_html(url),
      error = function(e) {
        if (debug) message("Could not read page: ", url)
        NULL
      }
    )
  }
  
  # Function to extract the base directory from a full URL if it contains a known press subdir
  extract_base_press_url <- function(url) {
    parts <- unlist(strsplit(url, "/"))
    last_valid_index <- suppressWarnings(
      max(which(tolower(parts) %in% possible_subdirs), na.rm = TRUE)
    )
    
    if (!is.finite(last_valid_index)) return(url)  # If no known subdir found, return as is
    return(paste(parts[1:last_valid_index], collapse = "/"))  # Return trimmed URL
  }
  
  # Function to find all press-related links on a given page
  find_all_press_links <- function(html_obj, base_url) {
    if (is.null(html_obj)) return(character(0))
    
    anchors <- html_elements(html_obj, "a[href]")
    if (length(anchors) == 0) return(character(0))
    
    txts  <- tolower(html_text(anchors, trim = TRUE))
    hrefs <- tolower(html_attr(anchors, "href"))
    
    # Identify relevant links
    idx_press <- grepl("press release", txts) | grepl("press-release|press-releases|pressroom|press-room", hrefs)
    idx_category_press <- grepl("category/congress_press_release|category/press-release|category/press-releases", hrefs)
    idx_news <- grepl("news", txts) & !grepl("newsletter", txts)
    
    keep_idx <- idx_press | idx_category_press | idx_news
    if (!any(keep_idx)) return(character(0))
    
    found_hrefs <- unique(url_absolute(html_attr(anchors[keep_idx], "href"), base_url))
    
    # Prioritize links containing "press-releases" or "category/congress_press_release" explicitly
    press_priority <- grepl("press-releases|press-release|pressroom|press-room|category/congress_press_release", found_hrefs)
    
    # Sort links to ensure most relevant appear first
    sorted_hrefs <- c(found_hrefs[press_priority], found_hrefs[!press_priority])
    
    # Extract only the base URL up to the relevant press directory
    return(unique(sapply(sorted_hrefs, extract_base_press_url)))
  }
  
  # Function to compare content of two pages (checks if they are distinct)
  is_different_page <- function(url1, url2) {
    pg1 <- try_read_html(url1)
    pg2 <- try_read_html(url2)
    if (is.null(pg1) || is.null(pg2)) return(FALSE)
    
    txt1 <- paste(xml_text(pg1), collapse = " ")
    txt2 <- paste(xml_text(pg2), collapse = " ")
    
    return(nchar(txt1) > 0 && nchar(txt2) > 0 && !identical(txt1, txt2))
  }
  
  # -------------------------------------------------------
  # Main Logic
  # -------------------------------------------------------
  
  main_page <- try_read_html(link)
  if (is.null(main_page)) {
    if (debug) message("Home page is not available. Returning NULL.")
    return(NULL)
  }
  
  # 1) Look for press links on the main page
  press_links_main <- find_all_press_links(main_page, link)
  if (length(press_links_main) > 0) {
    best_press_link <- press_links_main[1]
    if (debug) message("Found a direct press/news link on the main page: ", best_press_link)
    return(best_press_link)
  }
  
  # 2) Look for 'media-center' or 'media' links
  anchors_all <- html_elements(main_page, "a[href]")
  if (length(anchors_all) == 0) {
    if (debug) message("No anchors on main page. Returning NULL.")
    return(NULL)
  }
  
  all_hrefs <- url_absolute(html_attr(anchors_all, "href"), link)
  all_hrefs_lower <- tolower(all_hrefs)
  
  # Identify media-related links
  media_idx <- grepl("media-center", all_hrefs_lower) | grepl("media", all_hrefs_lower)
  media_links <- unique(all_hrefs[media_idx])
  
  if (length(media_links) == 0) {
    if (debug) message("No 'media' or 'media-center' link found. Returning NULL.")
    return(NULL)
  }
  
  # Prioritize "press-releases" and "category/congress_press_release" links over generic "media" links
  pr_idx <- grepl("press-releases|press-release|pressroom|press-room|category/congress_press_release", tolower(media_links))
  sorted_media_links <- c(media_links[pr_idx], media_links[!pr_idx])
  
  chosen_media_link <- sorted_media_links[1]  # Pick the best available
  
  # If media link already contains a press-related keyword, return the base version of it
  if (grepl("press-releases|press-release|category/congress_press_release", tolower(chosen_media_link))) {
    best_press_link <- extract_base_press_url(chosen_media_link)
    if (debug) message("Directly found press-related link: ", best_press_link)
    return(best_press_link)
  }
  
  # Read the "media" or "media-center" page
  if (debug) message("Reading 'media' page: ", chosen_media_link)
  media_page <- try_read_html(chosen_media_link)
  if (is.null(media_page)) {
    if (debug) message("No media page to parse. Returning NULL.")
    return(NULL)
  }
  
  # 3) Look for press links on the media page
  press_links_media <- find_all_press_links(media_page, chosen_media_link)
  if (length(press_links_media) > 0) {
    best_press_link <- press_links_media[1]
    if (debug) message("Found press link under the media page: ", best_press_link)
    return(best_press_link)
  }
  
  # 4) If no direct press links found, try common subdirectories
  media_base <- trim_slash(chosen_media_link)
  for (subdir in possible_subdirs) {
    test_url <- paste0(media_base, "/", subdir)
    if (is_different_page(media_base, test_url)) {
      best_press_link <- extract_base_press_url(test_url)
      if (debug) message("Found valid subdirectory page: ", best_press_link)
      return(best_press_link)
    }
  }
  
  if (debug) message("No relevant press release link found.")
  return(NULL)
}

# presser_page_finder("https://crane.house.gov", debug=T)

#presser_page_finder("https://mikerogers.house.gov", debug=T)
# 
# 
#presser_page_finder("https://steil.house.gov")
presser_page_finder("https://grijalva.house.gov", debug=T)

#presser_page_finder("https://crane.house.gov", debug=T)
```




### Node hunter
```{r}
# Loops through known nodes for elements (titles, dates, PR links and text)
node_hunter <- function(link, debug=F){
  
  # Check if link has https:// at the start, if not add it
  if(substr(link, 1, 8)!="https://") link <- paste0("https://", link)
  
  # Check if link is in valid format and date range is valid
  if(!grepl("https://[a-zA-Z0-9\\-]+\\.house\\.gov", link)){
    stop("Link is not of the form \"{name}.house.gov\" or \"https://{name}.house.gov\"")
  }
  
  # Sanitize input by removing extra forward slash at end of URL if present
  if(substr(link, nchar(link), nchar(link))=="/") link <- substr(link, 1, nchar(link)-1)
  
  # Initialize variables we'll return
  pr_page_link <- NA
  page_string <- NA
  page_index_start <- NA
  date_node <- NA
  date_node_type <- NA
  date_formats <- NA
  title_node <- NA
  title_node_type <- NA
  pr_link_node <- NA
  pr_link_node_type <- NA
  text_node <- NA
  text_node_type <- NA
  edgecase <- F # Indicator for non-paginated cases
  
  # Read in our webpage elements to look through
  nodes <- read_excel("nodes.xlsx")
  
  # Catch edge cases that require different scraping approach
  if(grepl("https://crane.house.gov", link)){
    
    edgecase <- T
    
    pr_page_link <- paste0(link, "/media")
    
    pr_page <- try(read_html(pr_page_link), silent=T)
    
    if(!inherits(pr_page, "try-error") & length(pr_page)==2){
      pr_page_link_home <- pr_page_link
    }
    else{
      stop("Edge case detected but failed to find PR page for: ", link)
    }
  }
  # Otherwise figure out link for the PR page and pagination
  else{
    
    # Find the link for the press release page
    pr_page_link <- presser_page_finder(link, debug=debug)
    
    if(is.na(link)) stop(paste0("Press release page could not be found for ", link))
    
    # Build the URL for the press releases page
    if (!grepl("^https?://", pr_page_link)) {
      # Remove trailing slashes from link
      base_link <- sub("/+$", "", link)
      
      # Remove leading slashes from pr_page_link
      relative_link <- sub("^/+", "", pr_page_link)
      
      # Combine with a single slash between them
      pr_page_link <- paste0(base_link, "/", relative_link)
    }
    
    # Save PR page home to return later
    pr_page_link_home <- pr_page_link
    
    ## FINDING PAGINATION FORMAT
    
    pagination <- nodes %>% filter(element=="page link")
    
    page_index_start <- NA
    page_string <- NA
    
    # Loop through press release page link formats until one works, then determine
    # if the pagination starts at 0 or 1
    for(p in pagination$string){
      page0 <- try(read_html(paste0(pr_page_link, p, 0)), silent=T)
      page1 <- try(read_html(paste0(pr_page_link, p, 1)), silent=T)
      page2 <- try(read_html(paste0(pr_page_link, p, 2)), silent=T)
      
      # A non-blank page will have length > 1
      if(length(page0)==1 & length(page0)==1) next
      else if(identical(page0 %>% html_text(), page1 %>% html_text) &
              identical(page1 %>% html_text(), page2 %>% html_text)){ next }
      else if(length(page0) > length(page1)){ page_index_start <- 0; page_string <- p; break }
      else if(length(page0) < length(page1)){ page_index_start <- 1; page_string <- p; break }
      else if(length(page0)==2 & length(page1)==2 & identical(page0 %>% html_text(), 
                                                              page1 %>% html_text())){
        page_index_start <- 1; page_string <- p; break 
      }
      else if(length(page0)==2 & length(page1)==2 & !identical(page0 %>% html_text(), 
                                                               page1 %>% html_text())){
        if(page0 %>% html_text() %>% str_detect("There are no records to display")){
          page_index_start <- 1; page_string <- p; break
        }
        else{ page_index_start <- 0; page_string <- p; break }
      }
      else stop("Determining starting page index failed for: ", link)
    }
    
    if(is.na(page_string)) stop(paste0("Pagination failed for ", link))
    
    # Build the press release page URL
    pr_page_link <- paste0(pr_page_link, page_string, page_index_start)
    
    if(debug) message("URL: ", pr_page_link)
  }
  
  ## FINDING DATE NODE
  
  date_nodes <- nodes %>% filter(element=="dates")
  date_node <- NA
  date_node_type <- NA
  date_formats <- NA
  date_attempt <- character(0) # Not NA b/c we differentiate successes by length
                               # Might have a page with 1 presser
  
  # Loop through date nodes until one works
  for(i in 1:nrow(date_nodes)){
    # Case when date can be found with xpath
    if(date_nodes$type[i]=="xpath"){
      date_attempt <- try(read_html(pr_page_link) %>% 
                          html_elements(xpath=date_nodes$string[i]) %>% 
                            html_text() %>% str_trim(), silent=T)
    }
    # Case when date can be found with CSS
    else{
      date_attempt <- try(read_html(pr_page_link) %>% 
                            html_elements(date_nodes$string[i]) %>% 
                            html_text() %>% str_trim(), silent=T)
    }
    
    if(length(date_attempt)==0 | inherits(date_attempt, "try-error")) next
    else{
      
      # Format the dates, also remove any likely non-date junk in our vector
      # The longest normally formatted date (i.e. "September 31st, 2025") is 20
      # characters long
      date_attempt <- gsub("  ", " ", date_attempt)
      date_attempt <- gsub("(\\d{1,2})(st|nd|rd|th)", "\\1", date_attempt, perl = TRUE)
      date_attempt <- date_attempt[nchar(date_attempt)<=20]
      
      if(length(date_attempt)==0) next
      
      # Detect the format of each scraped date
      date_formats <- detect_date_formats(date_attempt)
      
      # If they're all NA then try next node
      if(all(is.na(date_formats))) next
      # Otherwise we have our date node
      else{
        date_attempt <- date_attempt[which(!is.na(date_formats))] # Remove non-date elements
        date_node <- date_nodes$string[i]
        date_node_type <- date_nodes$type[i] 
        break
      }
    }
  }
  
  if(all(is.na(date_formats))) stop(paste0("No valid date node found for ", link))
  
  if(debug) message("Date node: ", date_node, 
                    "\nDate formats: ", paste(date_formats, collapse=" | "))
  
  ## FINDING TITLE LINK NODE
  
  title_nodes <- nodes %>% filter(element=="titles")
  title_node <- NA
  title_node_type <- NA
  title_attempt <- character(0)
  title_attempt_original_length <- NA
  
   # Loop through title nodes until one works
  for(i in 1:nrow(title_nodes)){
    
    # Case when title can be found with xpath
    if(title_nodes$type[i]=="xpath"){
      title_attempt <- try(read_html(pr_page_link) %>% 
                          html_elements(xpath=title_nodes$string[i]) %>% 
                            html_text() %>% str_trim(), silent=T)
    }
    # Case when title can be found with CSS
    else{
      title_attempt <- try(read_html(pr_page_link) %>% 
                            html_elements(title_nodes$string[i]) %>% 
                             html_text() %>% str_trim(), silent=T)
    }

    if(length(title_attempt)<1 | inherits(title_attempt, "try-error") |
       length(title_attempt) < length(date_attempt)) next 
    else{
      title_attempt_original_length <- length(title_attempt)
      
      # If title_attempt has more elements than date_attempt, grab the last elements
      # corresponding to the number of dates--sometimes headers are scraped before titles
      if(length(title_attempt) > length(date_attempt)){
        title_attempt <- title_attempt[(length(title_attempt) - length(date_attempt) + 1):length(title_attempt)]
      }
     
      title_node <- title_nodes$string[i]
      title_node_type <- title_nodes$type[i]
      break
    }
  }
  
  if(is.na(title_node)) stop(paste0("No valid title node found for ", link))
  
  if(debug) message("Title node: ", title_node)
  
  ## FINDING PR LINK NODE
  
  pr_link_attempt <- NA
  
  # Usually press release links are hyperlinked in the title so try that first
  pr_link_attempt <- try(read_html(pr_page_link) %>% 
                            html_elements(title_node) %>% html_attr("href") %>% 
                            str_trim(), silent=T)

  # If grabbing using the title node didn't work then loop through known
  # PR link nodes
  if(all(is.na(pr_link_attempt)) | inherits(pr_link_attempt, "try-error") |
     length(pr_link_attempt) > title_attempt_original_length){
    pr_link_nodes <- nodes %>% filter(element=="links")
    pr_link_node <- NA
    pr_link_attempt <- character(0)
    
    # Loop through PR link nodes until one works
    for(i in 1:nrow(pr_link_nodes)){
      
      # Case when date can be found with xpath
      if(pr_link_nodes$type[i]=="xpath"){
        pr_link_attempt <- try(read_html(pr_page_link) %>% 
                            html_elements(xpath=pr_link_nodes$string[i]) %>% 
                              html_text() %>% str_trim(), silent=T)
      }
      # Case when PR link can be found with CSS
      else{
        pr_link_attempt <- try(read_html(pr_page_link) %>% 
                               html_elements(pr_link_nodes$string[i]) %>% 
                               html_attr("href") %>% str_trim(), silent=T)
      }
  
      if(length(pr_link_attempt)<1 | inherits(pr_link_attempt, "try-error")) next 
      
      if(length(pr_link_attempt)<1 | inherits(pr_link_attempt, "try-error") |
       length(pr_link_attempt) < length(date_attempt)) next 
      else{
        # If pr_link_attempt has more elements than date_attempt, grab the last elements
        # corresponding to the number of dates--sometimes headers are scraped before pr_links
        if(length(pr_link_attempt) > length(date_attempt)){
          pr_link_attempt <- pr_link_attempt[(length(pr_link_attempt) - length(date_attempt) + 1):length(pr_link_attempt)]
        }
        pr_link_node <- pr_link_nodes$string[i]
        pr_link_node_type <- pr_link_nodes$type[i]
        break
      }
    }
    
  }
  # Otherwise PR link node and type are same as title
  else{
    # If pr_link_attempt has more elements than date_attempt, grab the last elements
    # corresponding to the number of dates--sometimes headers are scraped before pr_links
    if(length(pr_link_attempt) > length(date_attempt)){
      pr_link_attempt <- pr_link_attempt[(length(pr_link_attempt) - length(date_attempt) + 1):length(pr_link_attempt)]
    }
    
    pr_link_node <- title_node
    pr_link_node_type <- title_node_type
  }
  
  if(debug) message("PR link node:", pr_link_node)
  
  # Check if each PR link is a path or a complete URL and format accordingly
  pr_link_attempt1 <- format_pr_link(pr_link_attempt, pr_page_link)
  
  try_pr_link <- try(read_html(pr_link_attempt1[1]), silent=T)
  
  # If the first attempt fails it's probably because the individual press release
  # URLs don't include the path to the press releases page
  if(inherits(try_pr_link, "try-error")){
    pr_link_attempt2 <- format_pr_link(pr_link_attempt, link)

    # If that doesn't work, throw an error
    if(inherits(try(read_html(pr_link_attempt2[1]), silent=T), "try-error")){
      stop("Failed to build individual press release links for: ", link)
    }
    # Otherwise we now have our pr_link_attempt
    else pr_link_attempt <- pr_link_attempt2
  }
  else pr_link_attempt <- pr_link_attempt1
  
  if(debug) message("Example PR link: ", pr_link_attempt[1])
  
  
  # Check to make sure we have the same number of successfully parsed dates,
  # titles, and PR links
  # If not, then throw an error because something went wrong
  if(length(unique(c(sum(is.na(date_attempt)),  # Cheeky way to test equality of
                     sum(is.na(title_attempt)), # multiple values
                     sum(is.na(pr_link_attempt)))
                   ))!=1){
    if(debug){
      message("Dates: ", paste(date_attempt, collapse=" | "), "\n",
              "Titles:", paste(title_attempt, collapse=" | "), "\n",
              "Links: ", paste(pr_link_attempt, collapse=" | "))
    }
    stop("Number of dates, titles, and/or PR links does not match.")
  }
  
  ## FINDING PR TEXT NODE
  
  text_nodes <- nodes %>% filter(element=="text")
  text_link <- pr_link_attempt[1]
  text_node <- NA
  text_node_type <- NA
  text_attempt <- NA
  
  # Loop through text nodes until one works
  for(i in 1:nrow(text_nodes)){
    
    # Case when text can be found with xpath
    if(text_nodes$type[i]=="xpath"){
      text_attempt <- try(read_html(text_link) %>% 
                          html_element(xpath=text_nodes$string[i]) %>% 
                            html_text() %>% str_trim(), silent=T)
    }
    # Case when text can be found with CSS
    else{
      text_attempt <- try(read_html(text_link) %>% 
                            html_element(text_nodes$string[i]) %>% 
                             html_text() %>% str_trim(), silent=T)
    }
    
    if(is.na(text_attempt) | length(text_attempt)<1 | 
       inherits(text_attempt, "try-error")) next 
    else{
      text_node <- text_nodes$string[i]
      text_node_type <- text_nodes$type[i]
      break
    }
  }
  
  if(is.na(text_node)) stop(paste0("No valid PR text node found for ", link))
  
  if(debug) message("Text node: ", text_node)
  
  return(list(homepage_link=link,
              pr_page_link=pr_page_link_home,
              page_string=page_string,
              page_index_start=page_index_start,
              date_node=date_node,
              date_node_type=date_node_type,
              date_formats=date_formats,
              title_node=title_node,
              title_node_type=title_node_type,
              pr_link_node=pr_link_node,
              pr_link_node_type=pr_link_node_type,
              text_node=text_node,
              text_node_type=text_node_type,
              edgecase=edgecase # TRUE when legislator requires non-paginated scraping
              ))
  
}

node_hunter(link="hamadeh.house.gov", debug=T)

read_html("https://hamadeh.house.gov/media/press-releases") %>%
  html_elements(".views-row .font-weight-bold a") %>% html_attr("href")


# node_hunter(link="sewell.house.gov", debug=T)

# node_hunter(link="barrymoore.house.gov", debug=T)

# info_crane <- node_hunter(link="crane.house.gov", debug=T)
```

### Edgecase scraper
```{r}
edgecase_scraper <- function(info, start_date, end_date, 
                             pressers=data.frame(date=c(), title=c(), body=c(), 
                                                 tags=c(), url=c()),
                             clean_text=F, debug=F, progress=T){
  
  # Store scraping info in individual variables to make life easier
  homepage_link <- info$homepage_link
  pr_page_link <- info$pr_page_link
  date_node <- info$date_node
  date_node_type <- info$date_node_type
  date_formats <- info$date_formats
  title_node <- info$title_node
  title_node_type <- info$title_node_type
  pr_link_node <- info$pr_link_node
  pr_link_node_type <- info$pr_link_node_type
  text_node <- info$text_node
  text_node_type <- info$text_node_type
  
  start_date <- as.Date(start_date)
  end_date <- as.Date(end_date)
  
  # Get all the dates in the range
  date_range <- seq(from = start_date, to = end_date, by = "day")
  
  # Format the dates to be month year string we can use to navigate
  # press releases by month for legislators whose sites don't paginate
  monthyears <- unique(format(date_range, "/%Y/%m"))
  
  current_page <- NA
  
  for(m in monthyears){
    
    if(progress) message(ifelse(debug, "", "\014"), "Scraping pressers from: ", homepage_link, 
                       "    ", "/Year/Month: ", m)
    
    current_page <- try(read_html(paste0(homepage_link, m)), silent=T)
    
    if(inherits(current_page, "try-error")) next
    
    if(date_node_type=="css"){
      dates <- try(current_page %>% html_elements(date_node) %>% 
                            html_text() %>% str_trim, silent=T)
    }
    else{
      dates <- try(current_page %>% html_elements(xpath=date_node) %>% 
                            html_text() %>% str_trim, silent=T)
    }
    
    if(inherits(dates, "try-error") | length(dates)==0) next
    
    # Format the dates, also remove any likely non-date junk in our vector
    # The longest normally formatted date (i.e. "September 31st, 2025") is 20
    # characters long
    dates <- dates[which(!is.na(date_formats))] # Remove non-date elements
    dates <- gsub("  ", " ", dates)
    dates <- gsub("(\\d{1,2})(st|nd|rd|th)", "\\1", dates, perl = TRUE)
    dates <- dates[nchar(dates)<=20]
    dates <- mapply(function(x, fmt){ 
                      as.character(strptime(x, format = fmt, tz = ""))
                    }, 
                    dates, date_formats[which(!is.na(date_formats))])
    
    if(all(is.na(dates))){
      stop("Failed to format scraped dates for: ", homepage_link)
    }
    # Have we reached a page in our date range?
    if(head(dates, 1) > end_date & tail(dates, 1) > end_date) next
    else if(head(dates, 1) < start_date){
      # Stop paginating
      return(pressers)
    }
    else{
      # Page has pressers in our date range--scrape them

      # Get indexes for the dates within our range
      desired_dates <- which(dates >= start_date & dates <= end_date)
      
      # Format the dates so we can use them to navigate to press releases
      date_strings <- format(as.Date(dates[desired_dates]),
                                     "/%Y/%m/%d")
      
      
      # If there are pressers from the desired date range on the page then
      # get all the data we want
      if(length(desired_dates)>0){
        
        # Get titles
        if(title_node_type=="css") titles <- current_page %>% html_elements(title_node)
        else titles <- current_page %>% html_elements(xpath=title_node)
        
        titles <- titles %>% html_text() %>% str_trim()
        
        # If titles has more elements than dates, grab the last elements
        # corresponding to the number of dates--sometimes headers are scraped before titles
        if(length(titles) > length(dates)){
          titles <- titles[(length(titles) - length(dates) + 1):length(titles)]
        }
        
        # Build the PR URLs
        pr_links <- paste0(homepage_link, date_strings)
        
        # Subset to only pressers within date range
        titles <- titles[desired_dates]
        dates <- dates[desired_dates]
        
        texts <- sapply(pr_links, 
                          FUN=function(l){
                            if(text_node_type=="css") texts <- read_html(l) %>% html_elements(text_node)
                            else texts <- read_html(l) %>% html_elements(xpath=text_node)
                              
                            texts <- texts %>% html_text() %>% str_trim()
                          })

        # Get all known issue tag nodes
        tag_nodes <- read_excel("nodes.xlsx") %>% filter(element=="tags")
        
        tags <- c()
        tag <- NA

        # Try each known node for each press release
        # This is slow but not every press release will have a tag so can't
        # easily find node with node_hunter like other elements
        for(p in pr_links){
          for(i in 1:nrow(tag_nodes)){
            if(tag_nodes$type[i]=="css"){
              tag <- try(read_html(p) %>% html_elements(tag_nodes$string[i]),
                          silent=T)
            }
            else{
              tag <- try(read_html(p) %>% html_elements(xpath=tag_nodes$string[i]),
                          silent=T)
            }
            if(length(tag)!=1){
              if(length(tag)==0) tag <- NA
              else tag <- paste(tag, collapse=";")
            }
            else if(!inherits(tag, "try-error") | !is.na(tag) | 
               !identical(tag, character(0))){
              tag <- tag %>% html_text() %>% str_trim()
              break
            } 
            else tag <- NA
          }
          tags <- c(tags, tag)
        }

        # Add everything to the data frame
        pressers <- bind_rows(pressers, 
                          data.frame(date=dates, 
                                     title=titles, body=texts, 
                                     tags=tags, url=pr_links))
        }
    }
    
      
    }
  return(pressers)
}

# edgecase_scraper(info_crane, "2024-11-01", "2025-02-15")

# edgecase_scraper(info_crane, "2025-03-06", "2025-03-08")
```



### Member scraper
```{r}
# Recursively scrapes data for a single member
member_scraper <- function(info, start_date, end_date, page_index=0,
                           pressers=data.frame(date=c(), title=c(), 
                                               body=c(), tags=c(), url=c()),
                           page_limit=1000,
                           clean_text=F, # TODO: add option to have clean and raw text
                           debug=F, progress=T){
  
  # Catch when legislator requires non-paginated scraping
  if(info$edgecase==T){
    return(edgecase_scraper(info, start_date, end_date, pressers,
                            clean_text, debug, progress))
  }
  
  # Store scraping info in individual variables to make life easier
  homepage_link <- info$homepage_link
  pr_page_link <- info$pr_page_link
  page_string <- info$page_string
  page_index_start <- info$page_index_start
  date_node <- info$date_node
  date_node_type <- info$date_node_type
  date_formats <- info$date_formats
  title_node <- info$title_node
  title_node_type <- info$title_node_type
  pr_link_node <- info$pr_link_node
  pr_link_node_type <- info$pr_link_node_type
  text_node <- info$text_node
  text_node_type <- info$text_node_type
  
  # Data frame that will hold scraped pressers
  pressers <- data.frame(date=c(), title=c(), body=c(), tags=c(), url=c())

  if(page_index>page_limit){
    message("Page limit reached for: ", homepage_link)
    return(pressers)
  }
  
  page_index <- ifelse(page_index==0, page_index_start, page_index)
  
  if(progress) message(ifelse(debug, "", "\014"), "Scraping pressers from: ", homepage_link, 
                       "    ", "pg: ", page_index)
  
  current_page <- read_html(paste0(pr_page_link, page_string, page_index))
  
  if(date_node_type=="css") dates <- current_page %>% html_elements(date_node)
  else dates <- current_page %>% html_elements(xpath=date_node)
  
  dates <- dates %>% html_text() %>% str_trim()

  # Handle empty page case, i.e. when all the pages have been checked
    if(length(dates)==0) return(pressers)

    # Format the dates, also remove any likely non-date junk in our vector
    # The longest normally formatted date (i.e. "September 31st, 2025") is 20
    # characters long
    dates <- dates[which(!is.na(date_formats))] # Remove non-date elements
    dates <- gsub("  ", " ", dates)
    dates <- gsub("(\\d{1,2})(st|nd|rd|th)", "\\1", dates, perl = TRUE)
    dates <- dates[nchar(dates)<=20]
    dates <- mapply(function(x, fmt){ 
                      as.character(strptime(x, format = fmt, tz = ""))
                    }, 
                    dates, date_formats[which(!is.na(date_formats))])

    if(head(dates, 1) > end_date & tail(dates, 1) > end_date){
      # Haven't reached a page in our date range; recurse on the next page
      return(rbind(pressers, member_scraper(info, start_date, end_date,
                                            page_index + 1, pressers, 
                                            page_limit, clean_text, 
                                            debug, progress)))
    }
    else if(head(dates, 1) < start_date){
      # Base case: stop paginating
      return(pressers)
    }
    else{
      # Page has pressers in our date range--scrape them then recurse on next page

      # Get indexes for the dates within our range
      desired_dates <- which(dates >= start_date & dates <= end_date)

      # If there are pressers from the desired date range on the page then
      # get all the data we want
      if(length(desired_dates)>0){
        
        # Get titles
        if(title_node_type=="css") titles <- current_page %>% html_elements(title_node)
        else titles <- current_page %>% html_elements(xpath=title_node)
        
        titles <- titles %>% html_text() %>% str_trim()
        
        # If titles has more elements than dates, grab the last elements
        # corresponding to the number of dates--sometimes headers are scraped before titles
        if(length(titles) > length(dates)){
          titles <- titles[(length(titles) - length(dates) + 1):length(titles)]
        }
        
        # Get PR links
        if(pr_link_node_type=="css") pr_links <- current_page %>% html_elements(pr_link_node)
        else pr_links <- current_page %>% html_elements(xpath=pr_link_node)
        
        pr_links <- pr_links %>% html_attr("href")
        
        # Subset to only pressers within date range
        titles <- titles[desired_dates]
        pr_links <- pr_links[desired_dates]
        
        # Build the PR URLs
        pr_links <- format_pr_link(pr_links, pr_page_link)

        texts <- sapply(pr_links, 
                          FUN=function(l){
                            if(text_node_type=="css") texts <- read_html(l) %>% html_elements(text_node)
                            else texts <- read_html(l) %>% html_elements(xpath=text_node)
                              
                            texts <- texts %>% html_text() %>% str_trim()
                          })
        
        # Get all known issue tag nodes
        tag_nodes <- read_excel("nodes.xlsx") %>% filter(element=="tags")
        
        tags <- c()
        tag <- NA

        # Try each known node for each press release
        # This is slow but not every press release will have a tag so can't
        # easily find node with node_hunter like other elements
        for(p in pr_links){
          for(i in 1:nrow(tag_nodes)){
            if(tag_nodes$type[i]=="css"){
              tag <- try(read_html(p) %>% html_elements(tag_nodes$string[i]),
                          silent=T)
            }
            else{
              tag <- try(read_html(p) %>% html_elements(xpath=tag_nodes$string[i]),
                          silent=T)
            }
            if(length(tag)!=1){
              if(length(tag)==0) tag <- NA
              else tag <- paste(tag, collapse=";")
            }
            else if(!inherits(tag, "try-error") | !is.na(tag) | 
               !identical(tag, character(0))){
              tag <- tag %>% html_text() %>% str_trim()
              break
            } 
            else tag <- NA
          }
          tags <- c(tags, tag)
        }

        # Add everything to the data frame
        pressers <- bind_rows(pressers, 
                          data.frame(date=dates[desired_dates], 
                                     title=titles, body=texts, 
                                     tags=tags, url=pr_links))
        }
      }
  
  return(pressers)
}

info <- node_hunter(link="hamadeh.house.gov", debug=T)

member_scraper(info=info,
               start_date="2025-01-01", end_date=Sys.Date(),
                           pressers=data.frame(date=c(), title=c(), body=c(),
                                               tags=c(), url=c()),
                           debug=T, progress=T)

# TODO: Fix URL mismatch
```

### Main scraper
```{r}
# Main scraping function
presser_scraper <- function(links, start_date, end_date=Sys.Date(), 
                            clean_text=F, page_limit=1000, debug=F,
                            progress=T, remove_duplicates=F,
                            log_fails=F){
  
  if(start_date > end_date) stop("Start date is after end date.")
  
  if(as.Date(end_date) > Sys.Date()){
    end_date <- Sys.Date()
    warning("End date falls after current system date, setting end date to ",
            Sys.Date(), "\n")
  }
  
  pressers <- data.frame(date=NA, title=NA, body=NA, 
                         tags=NA, url=NA)
  

  if(!is.null(names(links))){ 
    pressers <- data.frame(name=NA, date=NA, title=NA, body=NA, 
                           tags=NA, url=NA)
  }
  
  if(log_fails) fails <- data.frame(URL=c(), error_message=c())
  
  for(i in seq_along(links)){
    scraped <- try(member_scraper(info=node_hunter(links[[i]], debug), 
                                  start_date=start_date, end_date=end_date, 
                                  page_index=0,
                                  pressers=pressers, page_limit=page_limit, 
                                  clean_text=clean_text, 
                                  debug=debug, progress=progress), 
                   silent=T)
    
    if(inherits(scraped, "try-error")){
      message(ifelse(debug, "", "\014"), "Scraping failed for: ", links[[i]])

      if(log_fails) fails <- bind_rows(fails, 
                                   data.frame(URL=links[[i]], 
                                              error_message=scraped[1] %>% 
                                                str_trim()))
    }
    else if(nrow(scraped)==0){
      message("No pressers found for: ", links[[i]])
      
      if(log_fails){
        fails <- bind_rows(fails, 
                           data.frame(URL=links[[i]], 
                                      error_message="No pressers found in date range"))
      }
    }
    else if(!is.null(names(links))){
      pressers <- bind_rows(pressers, scraped %>% mutate(name=names(links)[i]))
    }
    else pressers <- bind_rows(pressers, scraped)
  }
  
  if(log_fails){
    write.csv(fails, "fails.csv", row.names=F)
    message(nrow(fails), " failure(s) logged in fails.csv")
  }
  
  if(remove_duplicates) pressers <- distinct(pressers)
  
  # Remove rows with all NAs
  pressers <- pressers[rowSums(is.na(pressers)) < ncol(pressers), ]
  
  row.names(pressers) <- NULL
  
  return(pressers)
}

# presser_scraper(links=c(Schweikert="schweikert.house.gov",
#                         Barry="barrymoore.house.gov"),
#                 start_date="2025-01-01",
#                 end_date=Sys.Date(), 
#                 debug=F, progress=T, log_fails=F)

presser_scraper(links="grijalva.house.gov",
                start_date="2025-01-01",
                end_date=Sys.Date(),
                debug=T, progress=T, log_fails=F)
```

Failing V
Found a direct press/news link on the main page: https://grijalva.house.gov/category/congress_press_release/
URL: https://grijalva.house.gov/category/congress_press_release/?page=0
Date node: .info-date
Date formats: %B %d, %Y | %B %d, %Y | %B %d, %Y | %B %d, %Y | %B %d, %Y | %B %d, %Y | %B %d, %Y
Scraping failed for: grijalva.house.gov

```{r}
test <- presser_scraper(links=house_links[11:20],
                        start_date="2025-01-01",
                        end_date=Sys.Date(), 
                        debug=F, progress=T, log_fails=T)
```




```{r}
read_html("https://schweikert.house.gov/category/congress_press_release/") %>% html_elements(".title a") %>%
  html_attr("href")

read_html("https://barrymoore.house.gov/media/press-releases/rep-barry-moores-bill-deport-illegals-who-drive-under-influence-passes-house") %>% html_node(".evo-press-release__body") %>% html_text()


# EXAMPLE ISSUE TAG
read_html("https://palmer.house.gov/media-center/press-releases/palmer-bill-reverse-biden-harris-doe-rule-passes-house") %>% html_node(".evo-press-release__field-evo-issues") %>% 
  html_text() %>% str_trim()


info

temp <- read_html("https://barrymoore.house.gov/media/press-releases") %>% 
  html_elements(".font-weight-bold a")

read_html("https://barrymoore.house.gov/media/press-releases/media/press-releases/rep-barry-moore-supports-continuing-resolution-deliver-relief-producers-and") %>% html_element(".evo-press-release__body") %>% html_text()


temp <- try(read_html("https://obama.house.gov"))

temp[[1]] %>% str_trim()
```

Removed from nodes.xlsx for now:
dates	//*[contains(concat( \" \", @class, \" \" ), concat( \" \", \"col-auto\", \" \" ))]	xpath	F, G, J


TODO: FIND MORE NODES FOR ISSUE TAGS

TODO: CLEAN ISSUE TAGS

TODO: MAYBE ADD OPTION TO NOT SCRAPE TAGS SINCE IT'S O(N^2)

TODO: EXTRACT NAME, DISTRICT FROM WEBPAGE OR PRESSER TEXT, AT LEAST LAST NAME FROM URL

TODO: FIGURE OUT RUNNING ID SYSTEM

TODO: HAMADEH.HOUSE.GOV ISSUE TAGS, SAME ELEMENT AS TITLES (.font-weight-bold)
