---
title: "Scraper"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(rvest)
library(stringr)
```

# Scraper

```{r}
# Helper function that recursively scrapes press releases across pages within
# the given date range
page_scraper <- function(page_index, link, home, start_date, end_date,
                         template, debug=F){

  # Give the user a message to check progress
  cat("\014","Scraping from:", home, "   ", "pg:", page_index)
  
  # Add one day onto the start and end dates to ensure we don't miss any
  # pressers if there are multiple in one day and one happens to be at top or
  # bottom of the page
  start_date <- as.character(as.Date(start_date) - 1)
  end_date <- as.character(as.Date(end_date) + 1)
  
  # Data frame that will hold scraped pressers
  pressers <- data.frame(name=c(), title=c(), body=c(), url=c())
  
  if(template=="A"){
    page_link <- paste0(link, "?page=", page_index)
    
    page <- read_html(page_link)
    
    # Get the dates from the press releases previewed on the page
    dates <- page %>% html_nodes(".col-auto:nth-child(1)") %>% 
        html_text() %>% str_trim()
    
    # Handle empty page case, i.e. when all the pages have been checked
    if(length(dates)==0) return(pressers)
    
    # Format the dates
    dates <- sapply(dates, function(x) as.character(strptime(x, f <- "%B %d, %Y", tz = "")))
  
    if(head(dates, 1) > end_date & tail(dates, 1) > end_date){
      # Haven't reached a page in our date range; recurse on the next page
      return(rbind(pressers, page_scraper(page_index + 1, link, home, 
                                          start_date, end_date, template="A")))
    }
    else if(head(dates, 1) < start_date){
      # Base case: stop paginating
      return(pressers)
    }
    else{
      # Page has pressers in our date range--scrape them then recurse on next page
      
      # Get indexes for the dates within our range
      desired_dates <- which(dates >= start_date & dates <= end_date)
      
      titles <- page %>% html_nodes(".font-weight-bold a") %>% html_text()
      pr_links <- page %>% html_nodes(".font-weight-bold a") %>% 
        html_attr("href") %>% paste0(home, .)
  
      # Subset to only pressers within date range
      titles <- titles[desired_dates]
      pr_links <- pr_links[desired_dates]
      
      # Get the presser text
      texts <- sapply(pr_links, 
                      FUN=function(l){
                        read_html(l) %>% 
                          html_nodes(".evo-press-release__body") %>% 
                          html_text() %>% str_trim
                        })
      
      # Get the legislator's name and clean it
      name <- page %>% html_nodes(xpath="/html/head/meta[2]") %>% 
        html_attr("content")
      name <- gsub("U.S. Representative", "", name)
      name <- gsub("Representative", "", name)
      name <- gsub("U.S. Congressman", "", name)
      name <- gsub("U.S. Congresswoman", "", name)
      name <- gsub("Congressman", "", name)
      name <- gsub("Congresswoman", "", name)
      # Remove degrees but keep things like Jr.
      name <- gsub("\\s*,?\\s*(D\\.D\\.S\\.|PhD|M\\.D\\.|M\\.Sc\\.|LL\\.M\\.|
                   J\\.D\\.|B\\.Sc\\.|D\\.Phil\\.|Ed\\.D\\.|M\\.Eng\\.|\\w{1,3}
                   \\.\\w{1,3}\\.)", "", name)
      name <- str_trim(name)
      
      # Add everything to the data frame
      pressers <- rbind(pressers, 
                        data.frame(name=name, 
                                   date=dates[desired_dates], 
                                   title=titles, 
                                   body=texts, url=pr_links))
      
      # Recurse on next page
      return(rbind(pressers, page_scraper(page_index + 1, link, home, 
                                          start_date, end_date, template="A", debug=debug)))
    }
  }
  else if(template=="B"){
    page_link <- paste0(link, "&Page=", page_index)
    
    page <- read_html(page_link)
    
    # Get the dates from the press releases previewed on the page
    dates <- page %>% html_nodes("time") %>% html_text()
    
    # Handle empty page case, i.e. when all the pages have been checked
    if(length(dates)==0) return(pressers)
    
    # Format the dates
    dates <- sapply(dates, function(x) as.character(strptime(x, f <- "%B %d, %Y", tz = "")))
  
    if(head(dates, 1) > end_date & tail(dates, 1) > end_date){
      # Haven't reached a page in our date range; recurse on the next page
      return(rbind(pressers, page_scraper(page_index + 1, link, home, 
                                          start_date, end_date, template="B", debug=debug)))
    }
    else if(head(dates, 1) < start_date){
      # Base case: stop paginating
      return(pressers)
    }
    else{
      # Page has pressers in our date range--scrape them then recurse on next page
      
      # Get indexes for the dates within our range
      desired_dates <- which(dates >= start_date & dates <= end_date)
      
      titles <- page %>% html_nodes(".newsie-titler a") %>% html_text()
      pr_links <- page %>% html_nodes(".newsie-titler a") %>% html_attr("href") %>% 
        paste0(home,"/news/", .)
  
      # Subset to only pressers within date range
      titles <- titles[desired_dates]
      pr_links <- pr_links[desired_dates]
      
      # Get the presser text
      texts <- sapply(pr_links, 
                      FUN=function(l){
                        read_html(l) %>% 
                          html_nodes(".bodycopy") %>% 
                          html_text() %>% str_trim
                        })
      
      # Get the legislator's name and clean it
      name <- read_html(home) %>% html_nodes(xpath="/html/head/title") %>% 
        html_text() %>% str_trim()
      name <- gsub("U.S. Representative", "", name)
      name <- gsub("Representative", "", name)
      name <- gsub("U.S. Congressman", "", name)
      name <- gsub("U.S. Congresswoman", "", name)
      name <- gsub("Congressman", "", name)
      name <- gsub("Congresswoman", "", name)
      name <- gsub("\\s*,?\\s*(D\\.D\\.S\\.|PhD|M\\.D\\.|M\\.Sc\\.|LL\\.M\\.|
                   J\\.D\\.|B\\.Sc\\.|D\\.Phil\\.|Ed\\.D\\.|M\\.Eng\\.|\\w{1,3}
                   \\.\\w{1,3}\\.)", "", name) # Remove degrees but keep things like Jr.
      name <- str_trim(name)
      
      # Add everything to the data frame
      pressers <- rbind(pressers, 
                        data.frame(name=name, 
                                   date=dates[desired_dates], 
                                   title=titles, 
                                   body=texts, url=pr_links))
      
      # Recurse on next page
      return(rbind(pressers, page_scraper(page_index + 1, link, home, 
                                          start_date, end_date, template="B", debug=debug)))
    }
  }
  else if(template=="C"){
    page_link <- paste0(link, "/page/", page_index, "/")
    
    page <- read_html(page_link)
    
    # Get the dates from the press releases previewed on the page
    dates <- page %>% html_nodes(".info-date") %>% html_text()
    
    # Handle empty page case, i.e. when all the pages have been checked
    if(length(dates)==0) return(pressers)
    
    # Format the dates
    dates <- sapply(dates, 
                    function(x) as.character(
                      strptime(
                        gsub("\\b(\\d+)(st|nd|rd|th)\\b", "\\1", x), 
                        f <- "%B %d, %Y", tz = "")))
  
    if(head(dates, 1) > end_date & tail(dates, 1) > end_date){
      # Haven't reached a page in our date range; recurse on the next page
      return(rbind(pressers, page_scraper(page_index + 1, link, home, 
                                          start_date, end_date, template="C", debug=debug)))
    }
    else if(head(dates, 1) < start_date){
      # Base case: stop paginating
      return(pressers)
    }
    else{
      # Page has pressers in our date range--scrape them then recurse on next page
      
      # Get indexes for the dates within our range
      desired_dates <- which(dates >= start_date & dates <= end_date)
      
      titles <- page %>% html_nodes(".info-title") %>% html_text()
      pr_links <- page %>% html_nodes(".btn") %>% html_attr("href")
  
      # Subset to only pressers within date range
      titles <- titles[desired_dates]
      pr_links <- pr_links[desired_dates]
      
      # Get the presser text
      texts <- sapply(pr_links, 
                      FUN=function(l){
                        read_html(l) %>% html_nodes(".news-info__content") %>% 
                          html_text() %>% str_trim
                        })
      
      # Get the legislator's name and clean it
      name <- read_html(home) %>% 
        html_nodes("head > title:nth-child(9)") %>% 
        html_text() %>% str_trim()
      name <- gsub("U.S. Representative", "", name)
      name <- gsub("Representative", "", name)
      name <- gsub("U.S. Congressman", "", name)
      name <- gsub("U.S. Congresswoman", "", name)
      name <- gsub("Congressman", "", name)
      name <- gsub("Congresswoman", "", name)
      name <- gsub("Home - ", "", name)
      name <- gsub("\\s*,?\\s*(D\\.D\\.S\\.|PhD|M\\.D\\.|M\\.Sc\\.|LL\\.M\\.|
                   J\\.D\\.|B\\.Sc\\.|D\\.Phil\\.|Ed\\.D\\.|M\\.Eng\\.|\\w{1,3}
                   \\.\\w{1,3}\\.)", "", name) # Remove degrees but keep things like Jr.
      name <- str_trim(name)
      
      # Add everything to the data frame
      pressers <- rbind(pressers, 
                        data.frame(name=name, 
                                   date=dates[desired_dates], 
                                   title=titles, 
                                   body=texts, url=pr_links))
      
      # Recurse on next page
      return(rbind(pressers, page_scraper(page_index + 1, link, home, 
                                          start_date, end_date, template="C", debug=debug)))
    }
  }
  else if(template=="D"){
    
    page_link <- paste0(link, "?page=", page_index)
    
    page <- read_html(page_link)
    
    # Get the dates from the press releases previewed on the page
    dates <- page %>% html_nodes(".col-auto:nth-child(1)") %>% 
      html_text() %>% str_trim()
    
    # Handle empty page case, i.e. when all the pages have been checked
    if(length(dates)==0) return(pressers)
    
    # Format the dates
    dates <- sapply(dates, 
                    function(x) as.character(
                      strptime(x, f <- "%B %d, %Y", tz = "")))
  
    if(head(dates, 1) > end_date & tail(dates, 1) > end_date){
      # Haven't reached a page in our date range; recurse on the next page
      return(rbind(pressers, page_scraper(page_index + 1, link, home, 
                                          start_date, end_date, template="D", debug=debug)))
    }
    else if(head(dates, 1) < start_date){
      # Base case: stop paginating
      return(pressers)
    }
    else{
      # Page has pressers in our date range--scrape them then recurse on next page
      
      # Get indexes for the dates within our range
      desired_dates <- which(dates >= start_date & dates <= end_date)
      
      pr_links <- page %>% html_nodes("a") %>% html_attr("href")
      
      # Get rid of unwanted links
      pr_links <- pr_links[grepl("/media-center/press-releases/.+", pr_links)] %>% 
        paste(home, ., sep="") %>% unique()
      
      # Subset to only pressers within date range
      pr_links <- pr_links[desired_dates]
      
      # Get the presser titles (difficulty getting it from the landing page)
      titles <- sapply(pr_links, 
                      FUN=function(l){
                        read_html(l) %>% 
                          html_nodes("h1") %>% html_text() %>% str_trim
                        })
      
      # Get the presser text
      texts <- sapply(pr_links, 
                      FUN=function(l){
                        read_html(l) %>% 
                          html_nodes(".evo-press-release__body") %>% 
                          html_text() %>% str_trim
                        })
      
      # Get the legislator's name and clean it
      name <- read_html(home) %>% 
        html_nodes(xpath="/html/head/meta[6]") %>% 
        html_attr("content") %>% str_trim()
      name <- gsub("U.S. Representative", "", name)
      name <- gsub("Representative", "", name)
      name <- gsub("U.S. Congressman", "", name)
      name <- gsub("U.S. Congresswoman", "", name)
      name <- gsub("Congressman", "", name)
      name <- gsub("Congresswoman", "", name)
      name <- gsub("Home - ", "", name)
      name <- gsub("\\s*,?\\s*(D\\.D\\.S\\.|PhD|M\\.D\\.|M\\.Sc\\.|LL\\.M\\.|
                   J\\.D\\.|B\\.Sc\\.|D\\.Phil\\.|Ed\\.D\\.|M\\.Eng\\.|\\w{1,3}
                   \\.\\w{1,3}\\.)", "", name) # Remove degrees but keep things like Jr.
      name <- str_trim(name)
      
      # Add everything to the data frame
      pressers <- rbind(pressers, 
                        data.frame(name=name, 
                                   date=dates[desired_dates], 
                                   title=titles, 
                                   body=texts, url=pr_links))
      
      # Recurse on next page
      return(rbind(pressers, page_scraper(page_index + 1, link, home, 
                                          start_date, end_date, template="D", debug=debug)))
    }
  }
  else if(template=="E"){
    
    # Template E doesn't play nice with page index of 0
    if(page_index==0) page_index <- 1
    
    page_link <- paste0(link, "?page=", page_index)
    
    page <- read_html(page_link)
    
    # Get the dates from the press releases previewed on the page
    dates <- page %>% html_nodes(".recordListDate") %>% 
      html_text() %>% str_trim()
    
    # Handle empty page case, i.e. when all the pages have been checked
    if(length(dates)==0) return(pressers)
    
    # Format the dates
    dates <- sapply(dates, 
                    function(x) as.character(
                      strptime(x, f <- "%m/%d/%y", tz = "")))
  
    if(head(dates, 1) > end_date & tail(dates, 1) > end_date){
      # Haven't reached a page in our date range; recurse on the next page
      return(rbind(pressers, page_scraper(page_index + 1, link, home, 
                                          start_date, end_date, template="E", debug=debug)))
    }
    else if(head(dates, 1) < start_date){
      # Base case: stop paginating
      return(pressers)
    }
    else{
      # Page has pressers in our date range--scrape them then recurse on next page
      
      # Get indexes for the dates within our range
      desired_dates <- which(dates >= start_date & dates <= end_date)
      
      pr_links <- page %>% html_nodes(".ContentGrid") %>% html_attr("href") %>% 
        paste0(home,.)
      
      # Subset to only pressers within date range
      pr_links <- pr_links[desired_dates]
      
      # Get the presser titles
      titles <- page %>% html_nodes(".ContentGrid") %>% html_text()
      
      # Get the presser text
      texts <- sapply(pr_links, 
                      FUN=function(l){
                        read_html(l) %>% 
                          html_nodes(".post-content") %>% 
                          html_text() %>% str_trim
                        })
      
      # Get the legislator's name and clean it
      name <- read_html(home) %>% 
        html_nodes("head > title:nth-child(2)") %>% 
        html_text() %>% str_trim()
      name <- gsub("U.S. Representative", "", name)
      name <- gsub("Representative", "", name)
      name <- gsub("U.S. Congressman", "", name)
      name <- gsub("U.S. Congresswoman", "", name)
      name <- gsub("Congressman", "", name)
      name <- gsub("Congresswoman", "", name)
      name <- gsub("Home - ", "", name)
      name <- gsub("\\s*,?\\s*(D\\.D\\.S\\.|PhD|M\\.D\\.|M\\.Sc\\.|LL\\.M\\.|
                   J\\.D\\.|B\\.Sc\\.|D\\.Phil\\.|Ed\\.D\\.|M\\.Eng\\.|\\w{1,3}
                   \\.\\w{1,3}\\.)", "", name) # Remove degrees but keep things like Jr.
      name <- str_trim(name)
      
      # Add everything to the data frame
      pressers <- rbind(pressers, 
                        data.frame(name=name, 
                                   date=dates[desired_dates], 
                                   title=titles[desired_dates], 
                                   body=texts, url=pr_links))
      
      # Recurse on next page
      return(rbind(pressers, page_scraper(page_index + 1, link, home, 
                                          start_date, end_date, template="E", debug=debug)))
    }
  }
}

# Main scraping function
scraper <- function(link, start_date, end_date, debug=F){
  
  # Check if link is in valid format, date range is valid
  if(!grepl("https://[a-zA-Z0-9\\-]+\\.house\\.gov", link)){
    stop("Link is not of the form \"https://name.house.gov\"")
  }
  
  if(start_date > end_date){
    stop("Start date is after end date")
  }
  
  # Sanitize input by removing extra forward slash at end of URL if present
  if(substr(link, nchar(link), nchar(link))=="/") link <- substr(link, 1, nchar(link)-1)
  
  # Data frame that will hold scraped pressers
  pressers <- data.frame(name=c(), date=c(), title=c(), body=c(), url=c())
  
  # Determine template webpage uses
  # TODO: The logic here could likely be made less cumbersome
  template <- NA
  
  page_A <- try(read_html(paste0(link, "/media/press-releases")), 
                silent=T) # Try A
  page_B <- try(read_html(paste0(link, "/news/documentquery.aspx?DocumentTypeID=27")), 
                silent=T) # Try B
  page_C <- try(read_html(paste0(link, "/category/congress_press_release/")), 
                silent=T) # Try C
  page_D <- try(read_html(paste0(link, "/media-center/press-releases")), 
                silent=T) # Try D
  page_E <- try(read_html(paste0(link, "/press-releases")), 
                silent=T) # Try E
  
  page_lengths <- c(length(page_A), length(page_B), length(page_C), 
                    length(page_D), length(page_E))
  
  # Create a matrix with known lengths of each page template when the other
  # templates' landings are applied
  # When the call to read_html fails (403 or 404 error) it returns a length 1 error object
  # but otherwise the webpage is length 2
  # Rows are labelled with the actual page template
  # Columns are labelled with the tried page template
  length_matrix <- matrix(nrow=6, ncol=5,
                          data=c(2, 1, 1, 1, 1,
                                 1, 2, 1, 1, 1,
                                 1, 2, 1, 2, 1,
                                 2, 1, 2, 2, 2,
                                 1, 1, 1, 2, 1,
                                 1, 1, 1, 1, 2),
                          dimnames=list(c("A", "B", "B", "C", "D", "E"), 
                                        c("A", "B", "C", "D", "E")),
                          byrow=T
  )
  
  # Compare each row of matrix to the observed page lengths
  template <- rownames(length_matrix)[
    which(
      apply(length_matrix, 1, function(row) all(row == page_lengths))
    )
  ]
  
  # Throw an error if no rows match
  if(length(template) == 0) stop(paste0("Unknown template or bad URL for ", link)) 
  
  
  # With the template determined we can start scraping
  if(template=="A"){
    
    # Build the landing page link
    landing <- paste0(link, "/media/press-releases")
    
    # Do the scraping
    pressers <- rbind(pressers, 
                      page_scraper(page_index=0, link=landing, home=link, 
                                   start_date, end_date, template="A",
                                   debug=debug))
  }
  else if(template=="B"){
    
    # Build the landing page link
    landing <- paste0(link, "/news/documentquery.aspx?DocumentTypeID=27")
    
    # Do the scraping
    pressers <- rbind(pressers, 
                      page_scraper(page_index=0, link=landing, home=link, 
                                   start_date, end_date, template="B",
                                   debug=debug))
  }
  else if(template=="C"){
    # Build the landing page link
    landing <- paste0(link, "/category/congress_press_release/")
    
    # Do the scraping
    pressers <- rbind(pressers, 
                      page_scraper(page_index=0, link=landing, home=link, 
                                   start_date, end_date, template="C",
                                   debug=debug))
  }
  else if(template=="D"){
    # Build the landing page link
    landing <- paste0(link, "/media-center/press-releases")
    
    # Do the scraping
    pressers <- rbind(pressers, 
                      page_scraper(page_index=0, link=landing, home=link, 
                                   start_date, end_date, template="D",
                                   debug=debug))
  }
  else if(template=="E"){
    # Build the landing page link
    landing <- paste0(link, "/press-releases")
    
    # Do the scraping
    pressers <- rbind(pressers, 
                      page_scraper(page_index=0, link=landing, home=link, 
                                   start_date, end_date, template="E",
                                   debug=debug))
  }
  
  row.names(pressers) <- NULL
    
  return(pressers)
}

# Example usage

## Template A
# scraper(link="https://barrymoore.house.gov",
#          start_date="2023-07-20",
#          end_date="2023-10-21") #%>% View()

# scraper(link="https://biggs.house.gov",
#          start_date="2023-07-20",
#          end_date="2023-12-21") #%>% View()

## Template B
# scraper(link="https://gosar.house.gov",
#          start_date="2023-07-20",
#          end_date="2023-10-21") #%>% View()

# scraper(link="https://mikerogers.house.gov",
#          start_date="2023-07-20",
#          end_date="2023-10-21")

## Template C
scraper(link="https://grijalva.house.gov",
         start_date="2023-07-20",
         end_date="2023-10-21")

## Template D
# scraper(link="https://aderholt.house.gov",
#          start_date="2024-07-20",
#          end_date="2024-10-21")

## Template E
# scraper(link="https://sewell.house.gov/",
#          start_date="2024-07-20",
#          end_date="2024-10-21")

## Unknown Template/Bad URL
# scraper(link="https://obama.house.gov",
#          start_date="2023-07-20",
#          end_date="2023-10-21") #%>% View()
```

# Getting list of all House member domains
```{r}
websites <- read_html("https://www.house.gov/representatives") %>% 
  html_nodes(".views-field-value-5") %>% 
  html_nodes('a') %>% html_attr('href') %>% 
  sapply(FUN=function(x) sub("(house\\.gov).*", "\\1", x)) # Clean junk tacked on the end
```

# Test case: scraping all members' press releases since December 1
```{r}
sapply(websites[which(!websites %in% c("https://crane.house.gov", 
                                       "https://stanton.house.gov",
                                       "https://hamadeh.house.gov",
                                       "https://kiley.house.gov",
                                       "https://mikethompson.house.gov",
                                       "https://mcclintock.house.gov",
                                       "https://pelosi.house.gov",
                                       "https://simon.house.gov",
                                       "https://gray.house.gov",
                                       "https://kevinmullin.house.gov"))], 
       FUN=scraper, start_date="2024-12-01", end_date="2025-01-09", debug=T)
```

TODO:
- Templates: 
  - crane.house.gov date by date
  - stanton.house.gov
  - https://hamadeh.house.gov
    - new member not enough pressers to understand pagination
  - https://kiley.house.gov
  - https://mikethompson.house.gov
  - https://mcclintock.house.gov
  - https://pelosi.house.gov
  - https://simon.house.gov
  - https://gray.house.gov
  - https://kevinmullin.house.gov 
- Add better error handling for scraping process

# Template examples

## Template A

https://aderholt.house.gov/media-center/press-releases

https://biggs.house.gov/media/press-releases

https://barrymoore.house.gov/media/press-releases

Stout code
```{r}
get_main = function(links){
  press_page=read_html(links)
  
  press_info=press_page %>% html_nodes(".evo-press-release__body") %>% 
    html_text() %>% str_trim
  
  return(press_info)
}


moorepr=data.frame()
state="AL"
district=2

for(page_result in seq(from = 0 , to = 15, by = 1))
{
  link = paste0("https://barrymoore.house.gov/media/press-releases?page=", page_result)
  
  page = read_html(link)
  
  name = page %>% html_nodes(".font-weight-bold a") %>% html_text()
  
  links = page %>% html_nodes(".font-weight-bold a") %>% html_attr("href") %>% 
    paste("https://barrymoore.house.gov", ., sep="")
  
  date = page %>% html_nodes(".col-auto:nth-child(1)") %>% html_text()
  
  prpage = sapply(links, FUN=get_main)
  
  moorepr = rbind(moorepr, data.frame(state, district, name, date, prpage))
  
  print(paste("Page:", page_result))  
}

write.csv(moorepr, "C:/Users/bestf/OneDrive/Desktop/Press Releases/mooreal2.csv")
```



## Template B

https://mikerogers.house.gov/news/documentquery.aspx?DocumentTypeID=27

https://gosar.house.gov/news/documentquery.aspx?DocumentTypeID=27

Stout code
```{r}
get_main=function(links) {
press_page=read_html(links)
press_info=press_page%>% html_nodes(".bodycopy") %>% html_text() %>%str_trim
return(press_info)}

gosarpr=data.frame()
state="AZ"
district=4

for(page_result in seq(from = 0, to = 15, by = 1))
{
link= paste0("https://gosar.house.gov/news/documentquery.aspx?DocumentTypeID=27&Page=", page_result)
page=read_html(link)



name=page %>% html_nodes(".newsie-titler a") %>% html_text()
links=page %>% html_nodes(".newsie-titler a") %>% html_attr("href") %>% paste("https://gosar.house.gov/news/", ., sep="")
date=page %>%html_nodes("time") %>% html_text()
prpage=sapply(links, FUN=get_main)

gosarpr=rbind(gosarpr, data.frame(state, district, name, date, prpage))
 
}

 write.csv(gosarpr, "C:/Users/bestf/OneDrive/Desktop/Press Releases/gosarpraz4.csv")
```


## Template C

https://grijalva.house.gov/category/congress_press_release/

## Template D

https://aderholt.house.gov

## Template E

https://sewell.house.gov/


## Template F

https://crane.house.gov/
Note: was missing from Stout code